Parallel Multipoint Approximation Method for Large-Scale Optimization Problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2018-05-21 2018/PAVT_Toropov/PAVT2018_MAM.tex
FINAL

\documentclass[runningheads,a4paper]{llncs}
\usepackage{amssymb,amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{url}

@@

\bibitem{Toropov1989}
Toropov, V.:
\newblock Simulation approach to structural optimization.
\newblock Structural Optimization \textbf{1}, 37--46 (1989).

\bibitem{Toropov1992}
Toropov, V.:
\newblock Multipoint approximation method in optimization problems with expensive function values.
\newblock In: Sydow, A. (ed.) Proceedings of the 4th international symposium on Systems analysis and simulation,
pp.\,207--212, Elsevier,  (1992).

\bibitem{ToropovFilatov1993}
Toropov, V., Filatov, A., Polynkin, A.:
\newblock Multiparameter structural optimization using FEM and multipoint explicit approximations.
\newblock Structural Optimization \textbf{6}, 7--14 (1993).

\bibitem{ShahparPolynkinToropov2008}
Shahpar, S., Polynkin, A., Toropov, V.:
\newblock Large scale optimization of transonic axial compressor rotor blades.
\newblock In:  49th AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2008-2056
(2008).

\bibitem{PolynkinToropovShahpar2008}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Design optimization of aircraft engine components.
\newblock In: Proc. of 7th ASMO UK / ISSMO Conf. on Engineering Design Optimization. Process and Product Improvement
(2008).

\bibitem{PolynkinToropovShahpar2010}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Multidisciplinary optimization of turbomachinery based on metamodel built by genetic programming.
\newblock In: 13th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference
(2010).

\bibitem{KeulenToropovMarkine1996}
van Keulen, F., Toropov, V., Markine, V.:
\newblock Recent refinements in the multi-point approximation method in conjunction with adaptive mesh refinement.
\newblock In: McCarthy, J.M. (ed.) Proc. of ASME Design Engineering Technical Conferences and Computers
  in Engineering Conf., 1--12, ASME, Irvine CA (1996).

\bibitem{ToropovKeulenMarkine1996}
Toropov, V., van Keulen, F., Markine, V., de~Boer, H.:
\newblock Refinements in the multi-point approximation method to reduce the effects of noisy responses.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization,  pp.\,941--951, AIAA
(1996).

\bibitem{ToropovMarkineHolden1999}
Toropov, V., Markine, V., Holden, C.:
\newblock Use of mid-range approximations for optimization problems with functions of domain-dependent calculability.
\newblock In: 3rd ISSMO/UBCAD/UB/AIAA World Congress of Structural and Multidisciplinary Optimization (1999).

\bibitem{ToropovMarkine1996}
Toropov, V., Markine, V.:
\newblock The use of simplified numerical models as mid-range approximations.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization, pp.\,952--958 (1996).

\bibitem{ToropovAlvarez1998}
Toropov, V., Alvarez, L.:
\newblock Creation of multipoint approximations using genetic programming.
\newblock In: Parmee, I.C. (ed.) Adaptive Computing in Design and Manufacture, 3rd Int. Conf.,
   pp.\,21--24, PEDC, Dartington (1998).

\bibitem{PolynkinToropov2012}
Polynkin, A. Toropov, V.:
\newblock Mid-range metamodel assembly building based on linear regression for large scale optimization problems.
\newblock Structural and Multidisciplinary Optimization \textbf{45}(4), 515--527
(2012).

\bibitem{LancasterSalkauskas1981}
Lancaster, P. Salkauskas, K.:
\newblock Surfaces generated by moving least squares methods.
\newblock Mathematics of Computation \textbf{87}, 141--158 (1981).

\bibitem{Liszka1984}
Liszka, T.:
\newblock An interpolation method for an irregular net of nodes.
\newblock Int. J. Num. Meth. \textbf{20}, 1599--1612 (1984).

\bibitem{ChoiYounYang2001}
Choi, K., Youn, B., Yang, R.-J.:
\newblock Moving least squares method for reliability-based design optimization.
\newblock In: 4th World Congress of Structural and Multidisciplinary Optimization, Dalian, China
(2001).

\bibitem{ToropovSchrammSahaiJones2005}
Toropov, V., Schramm, U., Sahai, A., Jones, R., Zeguer, T.:
\newblock Design optimization and stochastic analysis based on the moving least squares method.
\newblock In: Herskovits, J., Mazorche, S., Canelas, A. (eds.) 6th World Congress of Structural and Multidisciplinary Optimization, art. no. 9412
(2005).

\bibitem{PolynkinToropov2010}
Polynkin, A. Toropov, V.:
\newblock Recognition of design variable inter-dependencies using cross-validated moving least-squares method.
\newblock In: Proceedings of the 51st AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2010-2985
(2010).

\bibitem{OllarToropovJones2014}
Ollar, J., Toropov, V., Jones. R.:
\newblock  Mid-range approximations in sub-spaces for MDO problems with disparate discipline attributes.
\newblock In: 15th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, AIAA, art. no. 2014-2437
(2014).

\bibitem{KeulenToropov1997}
van Keulen, F. Toropov, V.:
\newblock New developments in structural optimization using adaptive mesh refinement and multi-point approximations.
\newblock Engineering Optimization \textbf{29}, 217--234 (1997).

\bibitem{PolynkinToropov2008}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Adaptive and parallel capabilities in the multipoint approximation  method.
\newblock In: 12th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, AIAA, art. no. 2008-5803
(2008).

\bibitem{Vanderpllaats2001}
Vanderplaats, G.:
\newblock Multidiscipline Design Optimization.
\newblock Vanderplaats Research \& Development, Inc., Colorado Springs, (2001).

>>>>

\documentclass[a4paper]{llncs}
\usepackage{amssymb,amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{url}

@@

\bibitem{Toropov1989}
Toropov, V.:
\newblock Simulation approach to structural optimization.
\newblock Structural Optimization \textbf{1}, 37--46 (1989)

\bibitem{Toropov1992}
Toropov, V.:
\newblock Multipoint approximation method in optimization problems with expensive function values.
\newblock In: Sydow, A. (ed.) Proceedings of the 4th international symposium on Systems analysis and simulation,
pp.\,207--212, Elsevier,  (1992)

\bibitem{ToropovFilatov1993}
Toropov, V., Filatov, A., Polynkin, A.:
\newblock Multiparameter structural optimization using FEM and multipoint explicit approximations.
\newblock Structural Optimization \textbf{6}, 7--14 (1993)

\bibitem{ShahparPolynkinToropov2008}
Shahpar, S., Polynkin, A., Toropov, V.:
\newblock Large scale optimization of transonic axial compressor rotor blades.
\newblock In:  49th AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2008-2056
(2008)

\bibitem{PolynkinToropovShahpar2008}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Design optimization of aircraft engine components.
\newblock In: Proc. of 7th ASMO UK / ISSMO Conf. on Engineering Design Optimization. Process and Product Improvement
(2008)

\bibitem{PolynkinToropovShahpar2010}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Multidisciplinary optimization of turbomachinery based on metamodel built by genetic programming.
\newblock In: 13th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference
(2010)

\bibitem{KeulenToropovMarkine1996}
van Keulen, F., Toropov, V., Markine, V.:
\newblock Recent refinements in the multi-point approximation method in conjunction with adaptive mesh refinement.
\newblock In: McCarthy, J.M. (ed.) Proc. of ASME Design Engineering Technical Conferences and Computers
  in Engineering Conf., 1--12, ASME, Irvine CA (1996)

\bibitem{ToropovKeulenMarkine1996}
Toropov, V., van Keulen, F., Markine, V., de~Boer, H.:
\newblock Refinements in the multi-point approximation method to reduce the effects of noisy responses.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization,  pp.\,941--951, AIAA
(1996)

\bibitem{ToropovMarkineHolden1999}
Toropov, V., Markine, V., Holden, C.:
\newblock Use of mid-range approximations for optimization problems with functions of domain-dependent calculability.
\newblock In: 3rd ISSMO/UBCAD/UB/AIAA World Congress of Structural and Multidisciplinary Optimization (1999)

\bibitem{ToropovMarkine1996}
Toropov, V., Markine, V.:
\newblock The use of simplified numerical models as mid-range approximations.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization, pp.\,952--958 (1996)

\bibitem{ToropovAlvarez1998}
Toropov, V., Alvarez, L.:
\newblock Creation of multipoint approximations using genetic programming.
\newblock In: Parmee, I.C. (ed.) Adaptive Computing in Design and Manufacture, 3rd Int. Conf.,
   pp.\,21--24, PEDC, Dartington (1998)

\bibitem{PolynkinToropov2012}
Polynkin, A. Toropov, V.:
\newblock Mid-range metamodel assembly building based on linear regression for large scale optimization problems.
\newblock Structural and Multidisciplinary Optimization \textbf{45}(4), 515--527
(2012). doi:~10.1007/s00158-011-0692-1

\bibitem{LancasterSalkauskas1981}
Lancaster, P. Salkauskas, K.:
\newblock Surfaces generated by moving least squares methods.
\newblock Mathematics of Computation \textbf{87}, 141--158 (1981)

\bibitem{Liszka1984}
Liszka, T.:
\newblock An interpolation method for an irregular net of nodes.
\newblock Int. J. Num. Meth. \textbf{20}, 1599--1612 (1984)

\bibitem{ChoiYounYang2001}
Choi, K., Youn, B., Yang, R.-J.:
\newblock Moving least squares method for reliability-based design optimization.
\newblock In: 4th World Congress of Structural and Multidisciplinary Optimization, Dalian, China
(2001)

\bibitem{ToropovSchrammSahaiJones2005}
Toropov, V., Schramm, U., Sahai, A., Jones, R., Zeguer, T.:
\newblock Design optimization and stochastic analysis based on the moving least squares method.
\newblock In: Herskovits, J., Mazorche, S., Canelas, A. (eds.) 6th World Congress of Structural and Multidisciplinary Optimization, art. no. 9412
(2005)

\bibitem{PolynkinToropov2010}
Polynkin, A. Toropov, V.:
\newblock Recognition of design variable inter-dependencies using cross-validated moving least-squares method.
\newblock In: Proceedings of the 51st AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2010-2985
(2010)

\bibitem{OllarToropovJones2014}
Ollar, J., Toropov, V., Jones. R.:
\newblock  Mid-range approximations in sub-spaces for MDO problems with disparate discipline attributes.
\newblock In: 15th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, AIAA, art. no. 2014-2437
(2014). doi:~10.2514/6.2014-2437

\bibitem{KeulenToropov1997}
van Keulen, F. Toropov, V.:
\newblock New developments in structural optimization using adaptive mesh refinement and multi-point approximations.
\newblock Engineering Optimization \textbf{29}, 217--234 (1997). doi:~10.1080/03052159708940994

\bibitem{PolynkinToropov2008}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Adaptive and parallel capabilities in the multipoint approximation  method.
\newblock In: 12th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, AIAA, art. no. 2008-5803
(2008).doi:~10.2514/6.2008-5803

\bibitem{Vanderpllaats2001}
Vanderplaats, G.:
\newblock Multidiscipline Design Optimization.
\newblock Vanderplaats Research \& Development, Inc., Colorado Springs (2001)
